Total CD4 Data

### 2019-07-02 ICS_CD4.Rmd
Includes summed boolean and proportion figures

```{r}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean/")
cd4<-read.csv("ICS_CD4_clean.csv")
```

##Test and Return Significant Differences
This will run through each column, and test the relevant comparisons for statistical significance. It also corrects when multiple comparisons are made. Since Healthy Controls are only compared internally, they do not get included in the multiple testing comparison. The function only returns the comparisons that have an initial p-value less than 0.05, which reduces clutter. Everything else is insignificant.
```{r}
library(knitr)
#creates a list of character strings for each of the columns of interest
colnames<-names(dplyr::select(cd4, -X, -Sample, -Donor, -Stim, -TB, -SM))
for(col in colnames){#this will loop through each character string in the list
    a<-subset(cd4, cd4$Stim=="UN") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    b<-pvals_4(a, col)
    if(dim(b)[1]!=0)
    print(kable(b, caption=col)) #will return the output for each character string in the loop
}
```

@@

##Significant on Total CD4+ T cells
```{r, fig.width=12, fig.height=8}
data<-mutate_TB(filter(cd4, cd4$Stim=="UN"))
a<-plot_2(data, "disease", "CCR4")
b<-plot_2(data, "disease", "t_g_x_4")
c<-plot_2(data, "disease", "GATA3")
d<-plot_2(data, "disease", "GATA3.P_Tbet.N")
plot_grid(a,b,c,d, ncol=2)
```

##These are significant amongst Peptide-Specific CD4+ T cells
```{r}
b<-plot_2(data, "disease", "Tbet")+labs(y="Tbet+ Total CD4+ T cells (%)")
c<-plot_2(data, "disease", "t_x_x_4")+labs(y="CCR4+Tbet+ Total CD4+ T cells (%)")
d<-plot_2(data, "disease", "GATA3")+labs(y="GATA3+ Total CD4+ T cells (%)")
plot_grid(b,c,d, ncol=3)
```

@@

###MFI
```{r}
for(col in colnames[1:4]){#this will loop through each character string in the list
    x<-subset(cd4, cd4$Stim=="UN") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    y<-plot_6(x, "SM", col)+
        labs(subtitle=paste(gsub("_", " ", col), "on CD4+ T cells"), 
             caption="",
             x="",
             y=gsub("_", " ", col))
    print(y) #will return the output for each character string in the loop
}
```

###Surface Markers
```{r}
for(col in colnames[5:10]){#this will loop through each character string in the list
    x<-subset(cd4, cd4$Stim=="UN") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    name<-gsub(".P", "+", col)
    name<-gsub("_","", name)
    name<-gsub(".N", "-", name)
    y<-plot_6(x, "SM", col)+
        labs(subtitle=paste(name, "(% CD4+ T cells)"), 
             caption="",
             x="",
             y=paste(name, "(% CD4+ T cells)"))
    print(y) #will return the output for each character string in the loop
}
```

###Transcription Factors

As you can see there is one crazy looking "outlier" in GATA3 from NK2586. 
```{r}
for(col in colnames[11:16]){#this will loop through each character string in the list
    x<-subset(cd4, cd4$Stim=="UN") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    name<-gsub(".P", "+", col)
    name<-gsub("_","", name)
    name<-gsub(".N", "-", name)
    y<-plot_6(x, "SM", col)+
        labs(subtitle=paste(name, "(% CD4+ T cells)"), 
             caption="",
             x="",
             y=paste(name, "(% CD4+ T cells)"))
    print(y) #will return the output for each character string in the loop
}
```

#Side Note
This is the statistical evaluation of the data set without NK2586 the outlier GATA3 donor to see if it makes a difference.
```{r}
colnames2<-colnames[grep("GATA", colnames)]
for(col in colnames2){#this will loop through each character string in the list
    a<-filter(cd4, Stim=="UN", Donor!="NK2586") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    b<-pvals_6(a, col)
    if(dim(b)[1]!=0)
    print(kable(b, caption=col)) #will return the output for each character string in the loop
}
```

>>>>

```{r}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean/")
cd4<-read.csv("ICS_CD4_clean.csv")
grid.arrange(
    grid.arrange(
        grid.arrange(tableGrob(xtabs(~TB+SM, test)), HC_T, ncol=2),
        two, ncol=1), 
            b, ncol=2)```

##Test and Return Significant Differences
This will run through each column, and test the relevant comparisons for statistical significance. It also corrects when multiple comparisons are made. Since Healthy Controls are only compared internally, they do not get included in the multiple testing comparison. The function only returns the comparisons that have an initial p-value less than 0.05, which reduces clutter. Everything else is insignificant.
```{r}
library(knitr)
#creates a list of character strings for each of the columns of interest
colnames<-names(dplyr::select(cd4, -X, -X.1,-Sample, -Donor, -Stim, -TB, -SM))
for(col in colnames){#this will loop through each character string in the list
    a<-subset(cd4, cd4$Stim=="UN") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    b<-pvals_4(a, col)
    if(dim(b)[1]!=0)
    print(kable(b, caption=col)) #will return the output for each character string in the loop
}
```

@@

##Significant on Total CD4+ T cells
```{r, fig.width=16, fig.height=6}
data<-mutate_TB(filter(cd4, cd4$Stim=="UN"))
a<-plot_2(data, "disease", "CCR4")
b<-plot_2(data, "disease", "t_g_x_4")
c<-plot_2(data, "disease", "GATA3")
d<-plot_2(data, "disease", "GATA3.P_Tbet.N")
e<-plot_2(data, "disease", "GATA3CCR4")
plot_grid(a,b,ncol=2)
plot_grid(c,d,e,ncol=3)
```

##These are significant amongst Peptide-Specific CD4+ T cells
```{r, fig.width=12, fig.height=6}
b<-plot_2(data, "disease", "Tbet")+labs(y="Tbet+ Total CD4+ T cells (%)")
c<-plot_2(data, "disease", "t_x_x_4")+labs(y="CCR4+Tbet+ Total CD4+ T cells (%)")
d<-plot_2(data, "disease", "GATA3")+labs(y="GATA3+ Total CD4+ T cells (%)")
plot_grid(b,c,d, ncol=3)
```

@@

```{r, fig.width=16, fig.height=6}
test2<-melt(test, id.vars=c("Donor", "TB", "SM", "Stim"), measure.vars = grep("._._._.", names(cd4)))
test2<-filter(test2, variable!="x_x_x_x")
ggplot(test2, aes(x=variable, y=value, fill=TB, alpha=SM))+
    geom_boxplot()+
    scale_alpha_manual(values=c(0.5,1))+
    scale_fill_manual(values =c("#2166ac", "#b2182b"))+
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=8)+
    theme(legend.position="none")+
    labs(title="Lineage Marker Expression on Total CD4+ T cells",
         y="Frequency of Marker+ CD4+ T cells (%)")
```

###Surface Markers
```{r}
for(col in colnames[5:10]){#this will loop through each character string in the list
    x<-plot_filter(subset(cd4, cd4$Stim=="UN")) #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    name<-gsub(".P", "+", col)
    name<-gsub("_","", name)
    name<-gsub(".N", "-", name)
    y<-plot_with_all_stats(x, col)+
        labs(subtitle=paste(name, "(% CD4+ T cells)"), 
             caption="",
             x="",
             y=paste(name, "(% CD4+ T cells)"))
    print(y) #will return the output for each character string in the loop
}
```

###Transcription Factors
As you can see there is one crazy looking "outlier" in GATA3 from NK2586. 
```{r}
for(col in colnames[11:16]){#this will loop through each character string in the list
    x<-plot_filter(subset(cd4, cd4$Stim=="UN")) #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    name<-gsub(".P", "+", col)
    name<-gsub("_","", name)
    name<-gsub(".N", "-", name)
    y<-plot_with_all_stats(x, col)+
        labs(subtitle=paste(name, "(% CD4+ T cells)"), 
             caption="",
             x="",
             y=paste(name, "(% CD4+ T cells)"))
    print(y) #will return the output for each character string in the loop
}
```

##Combination Gates
```{r}
for(col in colnames[17:48]){#this will loop through each character string in the list
    x<-plot_filter(subset(cd4, cd4$Stim=="UN")) #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    y<-plot_with_all_stats(x, col)+
        labs(subtitle=col, 
           x="",
           y="")
    print(y) #will return the output for each character string in the loop
}
```

###MFI
```{r}
for(col in colnames[1:4]){#this will loop through each character string in the list
    x<-plot_filter(subset(cd4, cd4$Stim=="UN")) #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    y<-plot_with_all_stats(x, col)+
        labs(subtitle=paste(gsub("_", " ", col), "on CD4+ T cells"), 
             caption="",
             x="",
             y=gsub("_", " ", col))
    print(y) #will return the output for each character string in the loop
}
```
